\pagenumbering{arabic}
\chapter{Einleitung}
The standard interface between human and computer has for long years been mouse and keyboard. But with the advance of technology, new interfaceing methods were developed in the last few years.\\
Touch technology for interfacing with mobile devices and desktop computers has become a reliable technology and has been integrated into our everyday lives.
Advances in  capabilites of CPU as well as GPU hardware has build a foundation for the use of advanced AR and VR Technology. 3D and Stereoscopic rendering can now be accomplished even by mobile hardware (with some limitations) without the need of specifci hardware. For an intensly immersive experience VR Googles are used to explore digitally created worlds.\\
But with this level of immerivenes, a touch device or even a mouse and keyboard setup is rather hindering the user experience. First attempts of solving this problem came with the introduction of tracked controllers for the interaction with the digital world, but these can also only supply a fration of the capabilities of our natural interaction devices, namely the human hands.\\This thesis aims to display a method of combining the tracking of a physical object and the human hand(s) and merging this data into the digital space. The resulting experience for the user should be as natural as possible. Therefore  different systems for tracking of objects and bodyparts as well as the display of these in digital space will be presented and assessed. The results from the assessment wil be incorporated into a system prototype for testing with real users.