
\documentclass[10pt,twocolumn]{report}
\usepackage[utf8x]{inputenc}
\usepackage[twocolumn]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{wrapfig}
\usepackage[strings]{underscore}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{todonotes} 
\usepackage[english]{algorithm2e}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{float}
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\begin{document}
\title{RHOT-A real-time hand and object tracking
system with low cost consumer grade
hardware} % title
\maketitle
\begin{abstract}
Professional-grade hand and object racking systems are usually the result of long years of combining specialized hardware and software components to achieve a tracing solution. This comes at the cost of a high technical complexity of the systems and a corresponding high pricepoint. The underlying technical concepts of these systems can be boiled down to rather simple concepts. Therefore this paper will evaluate if it is possible to build a hand and object tracking system on low cost consumer grade hardware components. Therefor the most most common approach to spatial tracking, a stereoscopic camera setup, is chosen as the system base. To keep system cost low, a set of Raspberry Pi's with the matching Camera is used for image acquiring an processing. These processing units are linked to a master unit which takes care of stereoscopic depth calculations, the position value processing and the final rendering of a hand and object model in digital space. Several colored markers are assessed for the prototype application and compared in terms of tracking precision. A relatively new inverse kinematic framework as well as a novel method for input value filtering is also applied  and evaluated in the process.
The final results show that it is possible to achieve a tracking system solution with the used hardware components that has a suitable tracking update frequency and precision. The resulting prototype is good base for further research in terms of processing optimization.
\end{abstract}
\input{./chapter/01_introduction}
\input{./chapter/related_work}
\input{./chapter/02_Description_of_hand_in_digital_space.tex}
%\input{./chapter/05_System_prequisites}
\input{./chapter/06_System_conception}
\input{./chapter/07_System_Evaluation}



\newpage
% Bibliography
%\bibliographystyle{ACM-Reference-Format-Journals}
%\bibliography{literature}
                                % Sample .bib file with references that match those in
                                % the 'Specifications Document (V1.5)' as well containing
                                % 'legacy' bibs and bibs with 'alternate codings'.
                                % Gerry Murray - March 2012

\end{document}
% End of v2-acmtog-sample.tex (March 2012) - Gerry Murray, ACM
